---
title: "Week04_homework"
author: "Hilman Prakoso"
date: "2022-11-15"
output: html_document
---

# 1. Install countrycode package
```{r}
install.packages("countrycode")
```
# 2. Call The Library
```{r}
library(tidyverse)
library(here)
library(sf)
library(janitor)
library(countrycode)
```

# 3. Read both csv and shp file to R
## 3.1 Load the csv data using `read.csv`
### 3.1.1 Loading
```{r}
countrydata <- read_csv("HDR21-22_Composite_indices_complete_time_series.csv",
                locale=locale(encoding = "latin1"),
                na = " ",
                skip = 0
                )
```
### 3.1.2 Check the data
```{r}
class(countrydata)
```
```{r}
colnames(countrydata,
         head(15))
```


### 3.1.3 Selecting data only for Global Gender Inequality
```{r}
GlobalGenderInequality <- countrydata %>% 
  clean_names() %>% 
  select("iso3", "country", "gii_2010", "gii_2019")
```

### 3.1.4 make new column for gender inequality index difference
```{r}
GlobalGenderInequality_1 <- GlobalGenderInequality %>% 
  mutate(diff_gii=gii_2019-gii_2010)

```

### 3.1.5 Change the "iso3" column to 2 letter code


## 3.2 Load the shp file using `st_read`
```{r}
world_map <- st_read("World_Countries_(Generalized)/World_Countries__Generalized_.shp") %>% 
  clean_names()
```

# 4. Change the column name
- issue: countrydata use iso3 while world_map use iso2
- iso stands for International Standarization Organization, consensus to give code to every country. 3 means 3 letter, 2 means 2 letter
- we will use `countrycode` packages to change the country data
- using countrycode package
```{r}
GlobalGenderInequality_2 <- GlobalGenderInequality_1 %>% 
  mutate(iso2=countrycode(country, origin = 'country.name', destination = 'iso2c'))
  
```

# 5. Left Join the csv data and shp data
```{r}
GlobalGenderInequality_joined <- world_map %>% 
  left_join(.,
            GlobalGenderInequality_2,
            by = c("iso" = "iso2")
            )
```

